The SMT Competition 2015--2018

### 2019-08-19 2018/report/SMT-COMP.tex
Complete outline for Section 8 (Further Analysis)

Beyond the competition rankings, the competition data provides ample
opportunity for further analysis.  Here, we report on three additional
aspects: progress in solver performance, number of uniquely solved
benchmarks, and use of parallelism in SMT solvers.

>>>>

Beyond the competition rankings, the competition data provides ample
opportunity for further analysis.  Here, we report on several
additional aspects: progress in solver performance, number of uniquely
solved benchmarks, use of parallelism in SMT solvers, performance on
satisfiable versus unsatisfiable benchmarks, performance for a low
time limit, and the impact of benchmark families and of benchmarks
with unknown status.
